The Cluster Difference Imaging Photometric Survey (CDIPS). I. Methods \& Light Curves from TESS Sectors 1-5

### 2019-03-03 paper/ms.tex
paper updates

\title{Homogeneous Light Curves for Stars in Clusters from TESS:
Method \& Sector 1-4 Data Release}

@@

The TESS spacecraft began science operations on July 25, 2018.  To
keep its cameras pointed opposite the Sun, the spacecraft advances by
$\approx$$28$ degrees in ecliptic longitude every lunar month.  Data
acquired throughout each ``sector'' is downlinked at spacecraft
perigee through the Deep Space Network.  Verbose descriptions of the
spacecraft's design and operations are given by
\citet{ricker_transiting_2015} and the instrument handbook
\citep{vanderspek_2018}.

For us, the main data product of interest is the calibrated full frame
image (FFI).  Each TESS camera reads out every 2 seconds.  To produce
a manageable telemetric load, the resulting pixel values are averaged
by the onboard computer into 30 minute exposures. (An on-board cosmic
ray mitigation algorithm is applied.) Once transmitted to the ground,
the raw images are calibrated by the Science Processing Operations
Center.  The calibration process includes an overscan, bias, and dark
current correction, and also dividing out a flat field.  The details
are given by \citet{clarke_kepler_2017}, and the resulting science
data products are described by
\citet{tess_data_product_description_2018}.

@@

\subsection{Preparatory Steps}
\label{subsec:preparation}

@@

The first is to trim and mask the images.  We convert the calibrated
image from MAST into a \texttt{fitsh}-compatible image by retrieving
the image data, and omitting the uncertainty map. We then trim the
image to remove virtual rows and columns using the \texttt{SCIROWS},
\texttt{SCIROWE}, \texttt{SCCSA}, \texttt{SCCED}, header values.  We
mask out saturated stars using the `fiign` program with a fixed
saturation level of $2^{16}\,{\rm ADU}$.  As described by
\citet{Pal_2009}, the mask is metadata to the image, and is not ever
actually applied to the pixel values, except during specific image
processing steps that follow.  During masking, we also use the
algorithm described by \citet{Pal_2009} to extend masks beyond purely
saturated pixels to ``bloomed'' pixels horizontally and vertically
adjacent to the saturated pixels.  Finally, for frames with the
\texttt{DQUALITY} bit-flag set to 32~---~corresponding to the
``momentum dumps'' described by \citet{vanderspek_2018}~---~we mask
out the entire frame.  This removes on average a few frames per
sector. Through visual inspection, we see that the stars on these
frames are extremely smeared, and are unlikely to produce useful
science data.

>>>>

\title{
  The Cluster Difference Imaging Photometric Survey (CDIPS).
  I. Methods \& Light Curves from TESS Sectors 1-5
}

@@

The TESS spacecraft began science operations on July 25, 2018.  To
keep its cameras pointed opposite the Sun, the spacecraft advances by
$\approx$$28$ degrees in ecliptic longitude every lunar month.  Data
acquired throughout each ``sector'' are downlinked at spacecraft
perigee through the Deep Space Network.  Verbose descriptions of the
spacecraft's design and operations are given by
\citet{ricker_transiting_2015} and the instrument handbook
\citep{vanderspek_2018}.

For us, the main data product of interest is the calibrated full frame
image (FFI).  Each TESS camera reads out every 2 seconds.  To produce
a manageable telemetric load, the resulting pixel values are averaged
by the onboard computer into 30 minute exposures. An on-board cosmic
ray mitigation algorithm is applied (CITE: BERTA-THOMPSON). Once
transmitted to the ground, the raw images are calibrated by the
Science Processing Operations Center.  The calibration process
includes an overscan, bias, and dark current correction, and also
divides out a flat field.  The details are given by
\citet{clarke_kepler_2017}, and the resulting science data products
are described by \citet{tess_data_product_description_2018}.

@@

\subsection{Image Preparation \& Background Removal}
\label{subsec:preparation}

@@

First, we trim the images.  We convert the calibrated image from MAST
into a single-extension FITS image, trimmed to remove virtual rows and
columns using the \texttt{SCIROWS}, \texttt{SCIROWE}, \texttt{SCCSA},
and \texttt{SCCED} header values.

Second, we estimate the background of each frame.  We do this by
temporarily masking out pixels more than $2\sigma$ from the median,
and then passing a $48\times48$ median box filter over each pixel in
the image, using reflective boundary conditions. We subtract out this
smooth background estimate from each image.  This step helps mitigate
two unwanted image artifacts.  First, it removes a low-level glow
present in the corners of many images, which remains even after
flat-fielding \citep[see][\S 7.3.5]{vanderspek_2018}.  Second,
background subtraction removes scattered light patches from the Earth
and Moon, which vary in positions around the camera boresight over
each spacecraft orbit \citep[see][\S 7.3.1--7.3.4]{vanderspek_2018}.
The typical size of scattered light patches is greater than 32 pixels,
and their typical amplitude is $\sim 10\times$ the sky background
level.

% We found this background subtraction step to be particularly important
% in our subsequent difference imaging analysis. In its absense, the
% scattered light artifacts could introduce erroneous residuals into the
% kernel solution used to match reference and target images.  Including
% this step mitigated such effects, and helped produce clean
% subtractions.  Even after subtraction, a small fraction of frames also
% show sharp features (caustics) below our median box filter's size
% scale.  Such features may affect flux measurements at specific times
% in a small subset of lightcurves.

After subtracting the background, we mask out saturated stars using a
fixed saturation level of $8\times10^4\,{\rm ADU}$. This value was
chosen based on the onset of visible trails of bleeding charge, and is
slightly greater than the expected saturation level quoted by
\citet{vanderspek_2018}.  As described by \citet{Pal_2009}, our masks
are metadata to the image, and are only applied to the
pixel values during the specific image processing steps ({\it e.g.},
convolution) in which they are necessary. We also extend the masks
beyond purely saturated pixels to ``bloomed'' pixels horizontally and
vertically adjacent to the saturated pixels using the algorithm
described by \citet{Pal_2009}.

Finally, for frames with the \texttt{DQUALITY} bit-flag set to
32~---~corresponding to the ``momentum dumps'' described by
\citet{vanderspek_2018}~---~we mask out the entire frame.  This
removes on average a few frames per sector. Through visual inspection,
we see that the stars on these frames are extremely smeared, and are
unlikely to produce useful science data.
